---
title: "COVID19 Tracker"
output: 
  html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# load libraries
pkgs <- c("ggplot2", "plotly")
for(pkg in pkgs){library(pkg, character.only = TRUE)};rm(pkg, pkgs)

# read figures
# dir("../figures/")
```

[![GitHub forks](https://img.shields.io/github/forks/jdemello/StrapDown.js.svg?style=social&label=Fork&maxAge=2592000)](https://github.com/jdemello/covid19_tracker/StrapDown.js/network/)
[![GitHub stars](https://img.shields.io/github/stars/jdemello/StrapDown.js.svg?style=social&label=Star&maxAge=2592000)](https://github.com/jdemello/covid19_tracker/StrapDown.js/stargazers/)

_Last updated: `r format(Sys.time(), "%d %B, %Y (%H:%M:%S)")`_


### Mortality

#### Cumulative Reported Fatalities

The graph below is the tally of fatalities since starting from 10<sup>th</sup> confirmed death. The y-axis is log scaled.

```{r}
fig <- readRDS("../figures/deaths_acc.RDS")
fig
```

<br>
<br>

#### Cummulative Fatalities Adjusted by Population

<br>

```{r}
fig <- readRDS("../figures/mort_pm.RDS")
fig
```

<br>
<br>

#### Case Fatality Rate (CFR)

The observed fatalities divided by the total number of confirmed cases results in the case fatality rate (CFR).

```{r}
fig <- readRDS("../figures/cfr.RDS")
fig
```

<br>
<br>

### Sources

Confirmed cases and fatalities: [2019 Novel Coronavirus COVID-19 (2019-nCoV) Data Repository by Johns Hopkins CSSE](https://github.com/CSSEGISandData/COVID-19).

Population: [Countries in the world by population (2020)](https://www.worldometers.info/world-population/population-by-country/)